---
title: "Untitled"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---
heterogeneous multilayer network with hyper graph


## Multimodal Hypergraph Representation for Swedish population register:

In our project, we leverage Swedish population register data to construct a large-scale population network, where individuals are simultaneously embedded in multiple social contexts—including schools, workplaces, neighborhoods, and families. Rather than treating each context as an independent layer, we conceptualize the system as a multimodal hypergraph, where each hyperedge links all individuals jointly exposed to a specific social setting. This representation naturally captures higher-order group interactions and contextual co-presence, which are often obscured in pairwise or one-mode projections. It also allows us to flexibly encode heterogeneous types of ties and affiliations within a unified framework.

## Dynamic Network-Based Analysis:

Given the high density and complexity of the resulting network, traditional structural measures may fail to capture meaningful patterns of social proximity or segregation. We therefore incorporate dynamic processes—such as random walks and network embedding techniques—to better quantify social distances across demographic groups. These methods enable us to model how individuals are likely to encounter others through shared contexts and to learn low-dimensional representations that preserve both local clustering and global structural features. This approach is particularly useful for identifying cross-context exposure, estimating inter-group connectivity, and understanding the multilayered structure of social integration.

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
load_data()
knitr::opts_chunk$set(echo = TRUE)
# Setup for targets:

library(targets)
library(here)
tar_config_set(store = here("_targets"))

tar_load(g)

tar_load(result_df_RW)
tar_load(result_df_matrix)

```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2021] to ensure reproducibility and transparency. All code <!--and data--> are available at <SocDistRW>.

This is an example of a non-essential citation [@vanlissaWORCSWorkflowOpen2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
plot(g)
```

## Including Plots
```{r}

```

You can also embed plots, for example:

```{r pressure, echo=FALSE}


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
